Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-20 providence/sections/workload.tex
Final version for second shepherd draft

\begin{figure}
%\includegraphics[width=.5\textwidth]{real_time.png}
\includegraphics[width=.5\textwidth]{real_time_errorbars.png}
\caption{The real time as estimated by Equation~\ref{eq:real_time} for varying $p$ with expected values as estimated by our simulations. Error bars show the $0.25$ and $0.75$ quantiles. Unlike Figures \ref{fig:avg_bals}, \ref{fig:avg_bals_ratio}, and \ref{fig:with_round_workload}, the quantiles still differ for large $p$ because the first round size is no longer a constant; the number of ballots drawn in the first round in Fairfax County is variable.}
\label{fig:real_time}
\end{figure}

>>>>

\begin{figure}
%\includegraphics[width=.5\textwidth]{real_time.png}
\includegraphics[width=.5\textwidth]{real_time_errorbars.png}
\caption{The real time as estimated by Equation~\ref{eq:real_time} for varying $p$ with expected values as estimated by our simulations. Error bars show the $0.25$ and $0.75$ quantiles. Unlike Figures \ref{fig:avg_bals} and \ref{fig:with_round_workload}, the quantiles still differ for large $p$ because the first round size is no longer a constant; the number of ballots drawn in the first round in Fairfax County is variable.}
\label{fig:real_time}
\end{figure}
